Adopting agile in the large: motivations, success factors and challenges

### 2013-01-25 tex/article.tex
Institute and contacts
Abstract

\institute{Aalto University . . . Address . . .
\\ \email{kim.dikert@aalto.fi}, \email{maria.paasivaara@aalto.fi} }

@@

\begin{abstract}        % give a summary of your paper
Abstract: miksi on tärkeätä tutkia tätä?
-- Mitkä on pääasialliset löydökset?
The abstract should summarize the contents of the paper
using at least 70 and at most 150 words. It will be set in 9-point
font size and be inset 1.0 cm from the right and left margins.
There will be two blank lines before and after the Abstract.
%                         please supply keywords within your abstract
\keywords {agile, transformation, large scale, adopting agile}
\end{abstract}

@@

Typical challenges and and success factors reported in the studies are listed in
Table \ref{table:success}. In both cases the ability to align the organization
was a central factor in both cases. Challenges surface if not everyone is on
board with the change. Good ground for the change is created by strongly
communicating a clear vision and enabling everyone to participate. Resourcing
for the change was also seen both as a challenge and a success factor.
The studies show that allocating extra training and hiring of external consultants
facilitate the change.

@@

\begin{supertabular}{ l p{11.4cm} }
    {[}S1{]} & \bibentry{S1} \\  \shrinkheight{-1cm}
    {[}S2{]} & \bibentry{S2} \\ 
    {[}S3{]} & \bibentry{S3} \\ 
    {[}S4{]} & \bibentry{S4} \\ 
    {[}S5{]} & \bibentry{S5} \\ 
    {[}S6{]} & \bibentry{S6} \\ 
    {[}S7{]} & \bibentry{S7} \\ 
    {[}S8{]} & \bibentry{S8} \\ 
    {[}S9{]} & \bibentry{S9} \\
    {[}S10{]} & \bibentry{S10} \\ 
    {[}S11{]} & \bibentry{S11} \\ 
    {[}S12{]} & \bibentry{S12} \\  \shrinkheight{-1.4cm}
    {[}S13{]} & \bibentry{S13} \\ 
    {[}S14{]} & \bibentry{S14} \\ 
    {[}S15{]} & \bibentry{S15} \\ 
    {[}S16{]} & \bibentry{S16} \\ 
    {[}S17{]} & \bibentry{S17} \\ 
    {[}S18{]} & \bibentry{S18} \\ 
    {[}S19{]} & \bibentry{S19} \\ 
    {[}S20{]} & \bibentry{S20} \\ 
    {[}S21{]} & \bibentry{S21} \\ 
    {[}S22{]} & \bibentry{S22} \\ 
    {[}S23{]} & \bibentry{S23} \\ 
    {[}S24{]} & \bibentry{S24} \\ 
    {[}S25{]} & \bibentry{S25} \\ 
    {[}S26{]} & \bibentry{S26} \\ 
    {[}S27{]} & \bibentry{S27} \\ 
    {[}S28{]} & \bibentry{S28} \\ 
    {[}S29{]} & \bibentry{S29} \\ 
    {[}S30{]} & \bibentry{S30} \\ 
\end{supertabular}\end{document}

>>>>

\institute{Aalto University, School of Science,
Department of Computer Science and Engineering
\\ \email{kim-karol.dikert@aalto.fi}, \email{maria.paasivaara@aalto.fi}, \email{casper.lassenius@aalto.fi} }

@@

\begin{abstract}

Agile methods have become an appealing alternative for companies striving to
improve their performance. Agile methods have been originally designed for small
and individual teams. This poses challenges when introducing agile to large
organizations where development teams can not be autonomous. We reviewed 30
experience reports and case studies describing the process of taking agile
methods into use in large organizations. The primary motive for agile adoption
is the need to improve performance. For a successful transformation the entire
organization must be aligned and all organizational units must participate.
Creating an agile communityin the organization will help the change to stick.
Typical problems are misunderstanding of the agile model, and difficulties
coordinating the agile teams.

\keywords {agile, transformation, large scale, adopting agile}
\end{abstract}

@@

Typical challenges and and success factors reported in the studies are listed in
Table \ref{table:success}. The ability to align the organization was a central
factor for both success and challenges. Challenges surface if not everyone is on
board with the change. Good ground for the change is created by strongly
communicating a clear vision and enabling everyone to participate. Resourcing
for the change was also seen both as a challenge and a success factor.
The studies show that allocating extra training and hiring of external
consultants facilitate the change.

@@

\begin{supertabular}{ l p{11.4cm} }
    {[}S1{]} & \bibentry{S1} \\  \shrinkheight{-1cm}
    {[}S2{]} & \bibentry{S2} \\ 
    {[}S3{]} & \bibentry{S3} \\ 
    {[}S4{]} & \bibentry{S4} \\ 
    {[}S5{]} & \bibentry{S5} \\ 
    {[}S6{]} & \bibentry{S6} \\ 
    {[}S7{]} & \bibentry{S7} \\ 
    {[}S8{]} & \bibentry{S8} \\ 
    {[}S9{]} & \bibentry{S9} \\
    {[}S10{]} & \bibentry{S10} \\ 
    {[}S11{]} & \bibentry{S11} \\ 
    {[}S12{]} & \bibentry{S12} \\  \shrinkheight{-3cm}
    {[}S13{]} & \bibentry{S13} \\ 
    {[}S14{]} & \bibentry{S14} \\ 
    {[}S15{]} & \bibentry{S15} \\ 
    {[}S16{]} & \bibentry{S16} \\ 
    {[}S17{]} & \bibentry{S17} \\ 
    {[}S18{]} & \bibentry{S18} \\ 
    {[}S19{]} & \bibentry{S19} \\ 
    {[}S20{]} & \bibentry{S20} \\ 
    {[}S21{]} & \bibentry{S21} \\ 
    {[}S22{]} & \bibentry{S22} \\ 
    {[}S23{]} & \bibentry{S23} \\ 
    {[}S24{]} & \bibentry{S24} \\ 
    {[}S25{]} & \bibentry{S25} \\ 
    {[}S26{]} & \bibentry{S26} \\ 
    {[}S27{]} & \bibentry{S27} \\ 
    {[}S28{]} & \bibentry{S28} \\ 
    {[}S29{]} & \bibentry{S29} \\ 
    {[}S30{]} & \bibentry{S30} \\ 
\end{supertabular}\end{document}
